---
title: "Automating R Markdown"
author: "Claudia Donahue"
date: '2022-07-08'

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Assignment  

Our second project in this summer course was to use [this data](https://archive.ics.uci.edu/ml/datasets/Online+News+Popularity) to make several models to predict the number of times readers shared an article from Mashable. The data set was split into six channels--lifestyle, entertainment, business, social media, tech, and world--and our job was to automate a report for each channel from a single R Markdown file. We were also practicing building, testing, and comparing regression and ensemble models, using the `caret` package in R.  

## Our Solution  

You can see how our resulting six reports at [this link](https://cdonahu.github.io/st558-project2/), and delve deeper into how we solved the problem at our Github repo [here](https://github.com/cdonahu/st558-project2).  

## My Thoughts  

Happily, I do not think I would do a lot differently. I am glad to say we started working on this project as early as we could, and we had plenty of time to complete the work. I did notice that our predictive models were not making great predictions, so I might change the goal from predicting the dependent variable (number of shares) to predicting the *logarithm* of the number of shares. 

The most difficult part I encountered was in building the random forest model. I initially made the model so complex--both the tuning parameters and the repeated cross-validation--that the `caret::train()` function would run and run, never finishing. Once I simplified the model by reducing the *mtry* tuning parameter and no longer repeating the cross-validation, the model worked. 

## The Takeaway  

R Markdown is useful for so many reasons, and automating reports was within my reach. I think understanding this concept could be useful for me in the future. 

Thanks for reading!  

```{r, eval = FALSE, include=FALSE}
library(rmarkdown)
rmarkdown::render('./_Rmd/2022-07-08-Automating-R-Markdown.Rmd',
                  output_format = 'github_document',
                  output_dir = './_posts/',
                  output_options = list(
                    df_print = 'default',
                    html_preview = FALSE # to remove .html file creation
                    )
                  )
```