---
title: "API Interaction: A Vignette"
author: "Claudia Donahue"
date: '2022-06-26'

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.path = "../images/")
```

# The Vignette Assignment  

Our class was assigned to choose an API from a list and create a vignette, demonstrating to a user how to interact with that API. I initially chose the Pokemon API but had very limited success working with it and switched after a couple (wasted?) days. I ended up using a COVID-19 data API. 

I created a bunch of functions which allow a user to interact with the API and select options, like a country or timeline of interest. The user then gets a dataframe or a graph, depending which function. Then I explored the data further, using techniques we have been learning this term. 

# Reflections  

I found that I was left with a lot of questions. It was interesting to note that the United States has a much higher confirmed case count than any other country, but I wondered about record keeping and reporting. The same with the numbers of deaths. I also learned that a lot of the compelling data is behind a subscription fee, as I wished I had access to population and GDP data within the API, but I did not want to pay for it and did not have an excess of time to figure out how to match it up.  

I had trouble with this data set because it was not easy to categorize and explore the data the way we have been in other assignments. I had to add a new variable so that I had some interesting categories to compare across. Still, it was better than the Pokemon API, where I could not make a function return a decent dataframe in a reasonable amount of working time.  

I am happy to be getting more comfortable using github for version control. [Here](https://github.com/cdonahu/ST558-project-1) is a link to my repository for this project. 

# Next time  

Next time I have a project like this, I like to think I will start earlier and ask for help (probably) to make sure I can properly use the data I want to use (Pokemon -- to get my kids interested in data science). I also probably will not choose an API just based on whether I have to sign up for my own key. Who knows--I might even pay my own money for access to an API one day! 

## Last thing  
[Here](https://cdonahu.github.io/ST558-project-1/) is the link to my github pages repo for this project. I made it public on the due date for the project, as directed. 

```{r, eval = FALSE, include=FALSE}
library(rmarkdown)
rmarkdown::render('./_Rmd/2022-06-26-Vignette-blog-post.Rmd',
                  output_format = 'github_document',
                  output_dir = './_posts/',
                  output_options = list(
                    df_print = 'default',
                    html_preview = FALSE # to remove .html file creation
                    )
                  )
```