---
title: "Programming Background"
author: "Claudia Donahue"
date: '2022-06-06'
output: 'github_document'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "../images/")
```

## My Experience So Far  

The majority of my programming experience was in the Fall 2021 term in `ISE 535 Intro to Python`. I also did a weeklong course, `Intro to R Programming` in 2018, and I took an introductory course in `SAS` during the summer of 2021. Unfortunately, at work I usually use Excel, and my programming gains atrophy quickly. 

My thoughts on `R` so far in this course: I really like using Markdown in `R` to create a readable document. I think that this tool/skill will help me use `R` at work to create products for my coworkers who may not know anything about `R` or have any interest. And also for those who do, so they could understand and reproduce my work. 

I also like using RStudio with Github so far, for version control. I have had trouble working on projects with partners/groups because we are all working on one file and can't figure out how to best merge changes, so one team member does most of the work. 

I don't think I will miss much about other programming languages, especially Python since I am using it regularly in another course this summer! I do not consider R any more or less difficult than the other programming languages I have experienced, and it is much easier than foreign languages I have tried to learn, specifically Russian and French.    

## R Markdown Output  

Below, I am going to plot the Cars data set to make sure I can get the image to show up on my blog post: 

```{r, Plot of Cars data}
plot(cars, xlab = "Speed (mph)", ylab = "Stopping distance (ft)",
    las = 1, xlim = c(0, 25))
```

```{r, eval = FALSE, include=FALSE}
library(rmarkdown)
rmarkdown::render('./_Rmd/2022-06-06-Programming-Background-blog-post.Rmd',
                  output_format = 'github_document',
                  output_dir = './_posts/',
                  output_options = list(
                    df_print = 'default',
                    html_preview = FALSE # to remove .html file creation
                    )
                  )
```

