---
title: "End of the Term"
author: "Claudia Donahue"
date: '2022-07-18'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.path = '../images/')
```

## Using R for Data Science: My Thoughts  

I have really enjoyed working in R and using RStudio this term, after not having used it for several years. A lot of what I use in the future is going to depend on what I have access to in the workplace. I know there is a great chance I will be able to use R, so I expect to have a lot of opportunity to use it. If I had to make a prediction, I will probably just be battling the status quo of using Excel to handle anything related to data. 

It will be helpful that I now have experience using R Markdown to create .pdf and .html files to share reproducible work. 

## What Has Changed for Me  

Now that I have this recency and depth in R, I will have to decide when I feel it's appropriate to use R or Python, or another tool (probably Excel) at work. I also feel more equipped to work consistently on side projects or further self study outside of work, and I feel fortunate to know some experts at NC State, if I ever need to reach out.  


## My Next Exploration  

I am interested in trying out a competition, like Kaggle, or one through my employer. I also already have a request from a friend in my neighborhood to help them with some modeling. I am looking forward to seeing how I can help! 

I think at work, I will be exploring how to efficiently create dashboards useful for leaders in my organization. In my community, I like the idea of presenting publicly available data in ways others can better understand and draw conclusions. I am looking forward to completing my final project Shiny App with multiple pages and brainstorming similar things I could create as community tools.  





```{r code to generage blog post, eval = FALSE, include=FALSE}
library(rmarkdown)
rmarkdown::render('./_Rmd/2022-07-18-End-of-Course.Rmd',
                  output_format = 'github_document',
                  output_dir = './_posts/',
                  output_options = list(
                    df_print = 'default',
                    html_preview = FALSE # to remove .html file creation
                    )
                  )
```