---
title: "Update on How R Programming Is Going"
author: "Claudia Donahue"
date: '2022-06-27'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "../images/")
```

## So Far This Summer...  

We are just about halfway through the summer term (my final term in my program!), and I have made plenty of progress. We are done learning about how to program in R and the rest of the coursework will explore other skills. 

The coolest thing I have learned so far in the course is how to share my work using R markdown and Github Pages. Before this course, I had a brief introduction to programming in R about 4 years ago and had not used it much since then. Markdown was not a big part of that weeklong intro for me. I have found it really useful to create something I could then pass along to a colleague who wants to know how I got my results or how to replicate my work with their data.  

Another thing I am happy to have learned in R is how to create custom functions. This skill has been useful to develop so far my degree program when I want to use an algorithmic method to solve certain types of problems, but until now I have used other languages, like Python or Julia.  

Here's an example of a custom function that, given a numeric vector and a mean value to compare against, calculates the test statistic:  

```{r test stat function}

tStat <- function(vec, mean){
  
  tObs <- (mean(vec) - mean) / (sd(vec)/sqrt(length(vec)))
  
  return(tObs)
}
```


I look forward to learning more skills that will be useful in my career in operations research!


```{r, eval = FALSE, include=FALSE}
library(rmarkdown)
rmarkdown::render('./_Rmd/2022-06-27-Third-blog-post.Rmd',
                  output_format = 'github_document',
                  output_dir = './_posts/',
                  output_options = list(
                    df_print = 'default',
                    html_preview = FALSE # to remove .html file creation
                    )
                  )
```